A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-22 paper.tex
Added intro to toc

\section*{Introduction}

@@

\subsection*{Summary of Twisted Super Yang-Mills Theories}
In this section we'll summarize the results of Part \ref{classification_part} of the paper, in which we classify all twists of super Yang-Mills theories in dimensions 2 to 10.  We'll give this summary in two forms.  In Tables \ref{table_of_twists_16}, \ref{table_of_twists_8} and \ref{table_of_twists_4} we will display all the possible twists with a short name, and a precise description in terms of the moduli space of solutions to the twisted equations of motion.  We will also, in this subsection, give a short description of each twisted theory in more physical language, with references to where in the literature it was previously considered.

@@

\subsection*{Outline of the Paper}

@@

\subsubsection{Rank $(1, 1)$ partially topological twist}

@@

\subsubsection{Rank $(2, 2)$ twist}

@@

\subsubsection{Rank $(2,0)$ topological twist}
\label{sect:4d_2_donaldson}

@@

\subsubsection{Rank $(1,1)$ twist}
\label{sect:4d_2_11}

>>>>

\section*{Introduction} 
\label{sec:intro}
\addcontentsline{toc}{section}{Introduction}

@@

\subsection*{Summary of Twisted Super Yang-Mills Theories}
\addcontentsline{toc}{subsection}{Summary of Twisted Super Yang-Mills Theories}
In this section we'll summarize the results of Part \ref{classification_part} of the paper, in which we classify all twists of super Yang-Mills theories in dimensions 2 to 10.  We'll give this summary in two forms.  In Tables \ref{table_of_twists_16}, \ref{table_of_twists_8} and \ref{table_of_twists_4} we will display all the possible twists with a short name, and a precise description in terms of the moduli space of solutions to the twisted equations of motion.  We will also, in this subsection, give a short description of each twisted theory in more physical language, with references to where in the literature it was previously considered.

@@

\subsection*{Outline of the Paper}
\addcontentsline{toc}{subsection}{Outline of the Paper}

@@

\subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} partially topological twist}

@@

\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} Twist}

@@

\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
\label{sect:4d_2_donaldson}

@@

\subsubsection{Rank \texorpdfstring{$(1,1)$}{(1,1)} twist}
\label{sect:4d_2_11}
